---
title: "Evans et al. overlap analyses"
author: "Hannah Lucas-Clarke" 
date: "10/08/26"
---
Set Working directory and load function 

```{r}
setwd("/Users/clarkeh/OneDrive - The Francis Crick Institute/Projects/ASAP_Paper_Overlap/")
source("Overlap_func.R")
```

Loading Packages 

```{r}
#| label: Load packages
#| error: false
#| warning: false
#| echo: false
#| output: false 
library("tidyverse")
library("gprofiler2")
library("ComplexHeatmap")
library("org.Hs.eg.db")
library("AnnotationDbi")
library("knitr")
library("kableExtra")
library("gridExtra")
library("colorRamp2")
library("viridis")
library("GeneOverlap")
library("readxl")
library("janitor")
library("ComplexHeatmap")
library("circlize")
library("grid")
library("clusterProfiler")
library("svglite")
```

# Loading in Evans et al 2025 Bulk transcriptomics dataset

Using DEGs that are Padj < 0.05, no LFC cut off. 
Cortical Regions grouped 
Sub cortical Regions grouped 
Collapsed regions 

Universe is all the detected genes after cleaning - # 19,708

```{r}
#| label: Load bulk data
#| error: false
#| warning: false
#| echo: false
#| output: false 
universe_bulk <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>% 
  dplyr::select(SYMBOL) %>% unique() %>% nrow()

Cingulate_up <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>% 
  filter(sig_reg=="Significantly Upregulated") %>% 
  filter(tissue=="C_CTX") %>% 
  dplyr::select(SYMBOL) %>% 
  unique()
Frontal_Up <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>%
  filter(sig_reg=="Significantly Upregulated") %>% 
  filter(tissue=="F_CTX") %>% 
  dplyr::select(SYMBOL) %>% 
  unique()
Parietal_Up <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>%
  filter(sig_reg=="Significantly Upregulated") %>% 
  filter(tissue=="P_CTX") %>% 
  dplyr::select(SYMBOL) %>% 
  unique() 
Temporal_Up <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>%
  filter(sig_reg=="Significantly Upregulated") %>% 
  filter(tissue=="T_CTX") %>% 
  dplyr::select(SYMBOL) %>% 
  unique() 

cortical_up <- c(Cingulate_up$SYMBOL,Frontal_Up$SYMBOL,Parietal_Up$SYMBOL,Temporal_Up$SYMBOL) %>% unique()


Cingulate_down <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>% 
  filter(sig_reg=="Significantly Downregulated") %>% 
  filter(tissue=="C_CTX") %>% 
  dplyr::select(SYMBOL) %>% 
  unique()
Frontal_Down <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>%
  filter(sig_reg=="Significantly Downregulated") %>% 
  filter(tissue=="F_CTX") %>% 
  dplyr::select(SYMBOL) %>% 
  unique()
Parietal_Down <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>%
  filter(sig_reg=="Significantly Downregulated") %>% 
  filter(tissue=="P_CTX") %>% 
  dplyr::select(SYMBOL) %>% 
  unique() 
Temporal_Down <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>%
  filter(sig_reg=="Significantly Downregulated") %>% 
  filter(tissue=="T_CTX") %>% 
  dplyr::select(SYMBOL) %>% 
  unique()

cortical_down <- c(Cingulate_down$SYMBOL,Frontal_Down$SYMBOL,Parietal_Down$SYMBOL,Temporal_Down$SYMBOL) %>% unique()


Collapsed_up <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>% 
  filter(sig_reg=="Significantly Upregulated") %>% 
  filter(tissue=="Collapse-All Brain") %>% 
  dplyr::select(SYMBOL) %>% 
  unique()

Collapsed_down <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>% 
  filter(sig_reg=="Significantly Downregulated") %>% 
  filter(tissue=="Collapse-All Brain") %>% 
  dplyr::select(SYMBOL) %>% 
  unique()

caudate_up <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>% 
  filter(sig_reg=="Significantly Upregulated") %>% 
  filter(tissue=="CAU") %>% 
  dplyr::select(SYMBOL) %>% 
  unique()

caudate_down <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>% 
  filter(sig_reg=="Significantly Downregulated") %>% 
  filter(tissue=="CAU") %>% 
  dplyr::select(SYMBOL) %>% 
  unique()
SN_up <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>%
  filter(sig_reg=="Significantly Upregulated") %>% 
  filter(tissue=="SN") %>% 
  dplyr::select(SYMBOL) %>% 
  unique()
SN_down <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>% 
  filter(sig_reg=="Significantly Downregulated") %>% 
  filter(tissue=="SN") %>% 
  dplyr::select(SYMBOL) %>% 
  unique()



subcortical_up <- c(caudate_up$SYMBOL,SN_up$SYMBOL) %>% unique()
subcortical_down <- c(caudate_down$SYMBOL,SN_down$SYMBOL) %>% unique()

bulk_all <- list(Collapsed_up$SYMBOL,Collapsed_down$SYMBOL,cortical_up,cortical_down,subcortical_up,subcortical_down) 
names(bulk_all) <- c("Collapsed_up","Collapsed_down","Cortical_up","Cortical_down","Subcortical_up","Subcortical_down") 

bulk_up <- list(Collapsed_up$SYMBOL,cortical_up,subcortical_up) 
names(bulk_up) <- c("Collapsed_up","Cortical_up","Subcortical_up") 

rm(Cingulate_up,Cingulate_down,Frontal_Up,Frontal_Down,Parietal_Up,Parietal_Down,Temporal_Down,Temporal_Up,Collapsed_up,Collapsed_down,caudate_up,caudate_down,SN_up,SN_down,cortical_down,cortical_up,subcortical_down,subcortical_up)
```


# Loading in Evans et al 2025 single cell dataset 

Single cell 
P = Parietal 
C = Cingulate 
F = Frontal 
Level 2 annotation 

No LFC cut-off 

```{r}
#| label: Load single cell data 
#| error: false
#| warning: false
#| echo: false
#| output: false 
sc_universe <- readRDS("./OurData/SingleCell/de_X_sum_all_DE.rds") %>%
  janitor::clean_names() %>%
  filter(annot_level=="2") %>%
  dplyr::select(gene_sym) %>% 
  unique() %>% nrow()

sc_degs_immune_C <- readRDS("./OurData/SingleCell/de_X_sum_all_DE.rds") %>%
  janitor::clean_names() %>%
  dplyr::mutate(direction = case_when(
    log_fc<0 ~ "Down-regulated",
    log_fc>0 ~ "Up-regulated"
  )) %>%
  tidyr::separate(coef, into=c("tissue", "comparison")) %>%
  dplyr::mutate(comparison = case_when(comparison=="PDControl" ~ "Ctrl vs. PD")) %>%
  filter(annot_level=="2") %>%
  filter(clean_assay=="immune") %>%
  filter(tissue=="C") %>% 
  filter(adj_p_val<0.05)

sc_degs_immune_C_Up <- sc_degs_immune_C %>% filter(direction=="Up-regulated") %>% dplyr::select(gene_sym)  %>% unique()
sc_degs_immune_C_Down <- sc_degs_immune_C %>% filter(direction=="Down-regulated") %>% dplyr::select(gene_sym)  %>% unique()
rm(sc_degs_immune_C)

sc_degs_immune_P <- readRDS("./OurData/SingleCell/de_X_sum_all_DE.rds") %>%
  janitor::clean_names() %>%
  dplyr::mutate(direction = case_when(
    log_fc<0 ~ "Down-regulated",
    log_fc>0 ~ "Up-regulated"
  )) %>%
  tidyr::separate(coef, into=c("tissue", "comparison")) %>%
  dplyr::mutate(comparison = case_when(comparison=="PDControl" ~ "Ctrl vs. PD")) %>%
  filter(annot_level=="2") %>%
  filter(clean_assay=="immune") %>%
  filter(tissue=="P") %>% 
  filter(adj_p_val<0.05)

sc_degs_immune_P_Up <- sc_degs_immune_P %>% filter(direction=="Up-regulated") %>% dplyr::select(gene_sym)  %>% unique()
sc_degs_immune_P_Down <- sc_degs_immune_P %>% filter(direction=="Down-regulated") %>% dplyr::select(gene_sym)  %>% unique()
rm(sc_degs_immune_P)

sc_degs_immune_F <- readRDS("./OurData/SingleCell/de_X_sum_all_DE.rds") %>%
  janitor::clean_names() %>%
  dplyr::mutate(direction = case_when(
    log_fc<0 ~ "Down-regulated",
    log_fc>0 ~ "Up-regulated"
  )) %>%
  tidyr::separate(coef, into=c("tissue", "comparison")) %>%
  dplyr::mutate(comparison = case_when(comparison=="PDControl" ~ "Ctrl vs. PD")) %>%
  filter(annot_level=="2") %>%
  filter(clean_assay=="immune") %>%
  filter(tissue=="F") %>% 
  filter(adj_p_val<0.05)

sc_degs_immune_F_Up <- sc_degs_immune_F %>% filter(direction=="Up-regulated") %>% dplyr::select(gene_sym)  %>% unique()
sc_degs_immune_F_Down <- sc_degs_immune_F %>% filter(direction=="Down-regulated") %>% dplyr::select(gene_sym)  %>% unique()
rm(sc_degs_immune_F)

Immune_Up <- c(sc_degs_immune_C_Up$gene_sym,sc_degs_immune_F_Up$gene_sym,sc_degs_immune_P_Up$gene_sym) %>% unique()
Immune_Down <- c(sc_degs_immune_C_Down$gene_sym,sc_degs_immune_F_Down$gene_sym,sc_degs_immune_P_Down$gene_sym) %>% unique()

level2 <- list(Immune_Up,Immune_Down)
names(level2) <- list("Immune_Up","Immune_Down")

rm(sc_degs_immune_C_Up)
rm(sc_degs_immune_C_Down)
rm(sc_degs_immune_P_Up)
rm(sc_degs_immune_P_Down)
rm(sc_degs_immune_F_Up)
rm(sc_degs_immune_F_Down)

```


# Loading in external datasets of Disease Associated Microglia 

**Disease Associated Microglia: DAM (Keren-Shaul 2017)**
Had to convert to human symbols - did this with biomart gui 

```{r}
#| label: DAM
#| error: false
#| warning: false
#| echo: false
#| output: false 
DAM_Up <- read_csv("/Users/clarkeh/OneDrive - The Francis Crick Institute/Projects/ASAP_Paper_Overlap/MicrogliaPhenotypeLists/inputData/DAM_UP_Hs.csv",show_col_types = FALSE) %>% 
  dplyr::select(`Human gene name`) %>% unique() %>% na.omit()
DAM_Down <- read_csv("/Users/clarkeh/OneDrive - The Francis Crick Institute/Projects/ASAP_Paper_Overlap/MicrogliaPhenotypeLists/inputData/DAM_down_Hs.csv",show_col_types = FALSE) %>% 
  dplyr::select(`Human gene name`) %>% unique() %>% na.omit()
```

**Human Alzheimer's Microglia: HAM (Srinivasan 2020)**

```{r}
#| label: HAM
#| error: false
#| warning: false
#| echo: false
#| output: false 
HAM_Up <- read.csv("./MicrogliaPhenotypeLists/inputData/HAM_list.csv") %>% filter(Human.AD.Myeloid=="Up") %>% dplyr::select(Gene.Symbol) %>% unique()
HAM_Down <- read.csv("./MicrogliaPhenotypeLists/inputData/HAM_list.csv") %>% filter(Human.AD.Myeloid=="Down") %>% dplyr::select(Gene.Symbol) %>% unique()
```


**HuMiCA (Martins-Ferreira 2025) **
Combines data from 19 experiments across different diseases 
pseudo bulked 
disease-inflammatory macrophages - DIM (cluster 2) - AD and LBD 
disease associate microglia - DAM (clusters 1, 3, 5, 6) - AD and LBD 

Only has upregulated genes (No LFC cut off)

```{r}
#| label: Humica
#| error: false
#| warning: false
#| echo: false
#| output: false 
Humica_DAM_AD_Up <- read_csv("/Users/clarkeh/OneDrive - The Francis Crick Institute/Projects/ASAP_Paper_Overlap/MicrogliaPhenotypeLists/inputData/Humica_DAM.csv", show_col_types = FALSE) %>% 
  filter(Group=="AD") %>% filter(log2FoldChange>0) %>% dplyr::select(Gene) %>% unique()
Humica_DAM_LBD_Up <- read_csv("/Users/clarkeh/OneDrive - The Francis Crick Institute/Projects/ASAP_Paper_Overlap/MicrogliaPhenotypeLists/inputData/Humica_DAM.csv",show_col_types = FALSE) %>% 
  filter(Group=="LBD") %>% filter(log2FoldChange>0) %>% dplyr::select(Gene) %>% unique()
Humica_DIM_AD_Up <- read_csv("/Users/clarkeh/OneDrive - The Francis Crick Institute/Projects/ASAP_Paper_Overlap/MicrogliaPhenotypeLists/inputData/Humica_DIM.csv",show_col_types = FALSE) %>% 
  filter(Group=="AD") %>% filter(log2FoldChange>0) %>% dplyr::select(Gene) %>% unique()
Humica_DIM_LBD_Up <- read_csv("/Users/clarkeh/OneDrive - The Francis Crick Institute/Projects/ASAP_Paper_Overlap/MicrogliaPhenotypeLists/inputData/Humica_DIM.csv",show_col_types = FALSE) %>% 
  filter(Group=="LBD") %>% filter(log2FoldChange>0) %>% dplyr::select(Gene) %>% unique()
```

Now combining these external DAM datasets into a list so i can do the overlaps - need symbols 

```{r}
#| label: combine datasets
#| error: false
#| warning: false
#| echo: false
#| output: false 
all_external <- list(DAM_Up$`Human gene name`,
                     DAM_Down$`Human gene name`,
                     HAM_Up$Gene.Symbol,
                     HAM_Down$Gene.Symbol,
                     Humica_DAM_AD_Up$Gene,
                     Humica_DAM_LBD_Up$Gene,
                     Humica_DIM_AD_Up$Gene,
                     Humica_DIM_LBD_Up$Gene)
names(all_external) <- c("DAM_Up",
                         "DAM_Down", 
                         "HAM_Up",
                         "HAM_Down",
                         "Humica_DAM_AD_Up",
                         "Humica_DAM_LBD_Up",
                         "Humica_DIM_AD_Up",
                         "Humica_DIM_LBD_Up")

```


# First overlap analysis our bulk data vs. extrnal DAM datasets 

This is doing all bulk overlapping with all external
adjusting within external datasets 
Includes both up and down 
universe is the bulk dataset all detected genes 
calculates Szymkiewicz–Simpson overlap intersection/min of A and B 
 

```{r}
#| label: Overlap bulk. up and down
#| error: false
#| warning: false
#| echo: false
#| output: true
result1 <- Overlap_HLC_func(list1 = bulk_all,
                            list2=all_external,
                            universe=universe_bulk,
                            nadj=3,
                            trunc=FALSE, 
                            plot=FALSE,
                            save_res = "./results/result1.csv")
```

Just visualizing the Up regulated signatures - same stats underneath 

```{r}
#| label: Overlap bulk ploting just Up 
#| error: false
#| warning: false
#| echo: false
#| output: true
result2 <- Overlap_HLC_func(list1 = bulk_all,
                            list2=all_external,
                            universe=universe_bulk,
                            nadj=3,
                            trunc=TRUE, 
                            plot=TRUE,
                            trunc_col = c("DAM_Down", "HAM_Down"),
                            trunc_row = c("Collapsed_down", "Cortical_down", "Subcortical_down"),
                            plotmax = 0.5,
                            list1_title = "Bulk RNASeq PD vs. Control - Upregulated",
                            split = c(rep("Keren-Shaul 2017", 1),rep("Srinivasan 2020", 1),rep("Martins-Ferreira 2025", 4)),
                            tidy_col = c("DAM", "HAM", "HuMicA AD DAM", "HuMicA LBD DAM", "HuMicA AD DIM", "HuMicA LBD DIM"),
                            tidy_row = c("Collapsed Brain", "Cortical", "Subcortical"),
                            save_res = "./results/result2.csv",
                            save_fig = "./results/result2.svg",
                            width_fig = 7,
                            height_fig = 4)
```


#Next overlapping single cell data to the external datasets

Level 2 single cell and all external datasets 
Adjusting within the external datasets 
Includes both up and down 
universe is the sc dataset all detected genes 
calculates Szymkiewicz–Simpson overlap intersection/min of A and B 

```{r}
#| label: Overlap - heatmap level2
#| error: false
#| warning: false
#| echo: false
#| output: true
result3 <- Overlap_HLC_func(list1 = level2,
                            list2=all_external,
                            universe=sc_universe,
                            nadj=3,
                            trunc=FALSE, 
                            plot=FALSE,
                            save_res = "./results/result3.csv")
```

Plotting up only same underlying stats just visualized differently 

```{r}
result4 <- Overlap_HLC_func(list1 = level2,
                            list2=all_external,
                            universe=sc_universe,
                            nadj=3,
                            trunc=TRUE, 
                            plot=TRUE,
                            trunc_col = c("DAM_Down", "HAM_Down"),
                            trunc_row = c("Immune_Down"),
                            plotmax = 0.5,
                            list1_title = "Single Cell RNAseq PD vs. Control",
                            split = c(rep("Keren-Shaul 2017", 1),rep("Srinivasan 2020", 1),rep("Martins-Ferreira 2025", 4)),
                            tidy_col = c("DAM", "HAM", "HuMicA AD DAM", "HuMicA LBD DAM", "HuMicA AD DIM", "HuMicA LBD DIM"),
                            name_trunc = "Immune",
                            save_res = "./results/result4.csv",
                            save_fig = "./results/result4.svg",
                            width_fig = 7,
                            height_fig = 4)
```


#Next moving to the invitro datasets 

1. Loading Cell Data (3 datasets) iMGLS + 
  Monomers 
  Mutation 
  Oligomers 

```{r}
monomer_wt_up <- read.csv("./OurData/Invitro/protein_coding_monomer.csv") %>% 
  filter(reg=="up") %>% filter(comparison=="wt vs ut") %>% unique() %>% dplyr::select(external_gene_name)
monomer_wt_up <- monomer_wt_up[monomer_wt_up != ""]

monomer_wt_down <- read.csv("./OurData/Invitro/protein_coding_monomer.csv") %>% 
  filter(reg=="down") %>% filter(comparison=="wt vs ut") %>% unique() %>% dplyr::select(external_gene_name)
monomer_wt_down <- monomer_wt_down[monomer_wt_down != ""]

monomer_a53t_UT_up <- read.csv("./OurData/Invitro/protein_coding_monomer.csv") %>% 
  filter(reg=="up") %>% filter(comparison=="a53t vs ut") %>% unique() %>% dplyr::select(external_gene_name)
monomer_a53t_UT_up <- monomer_a53t_UT_up[monomer_a53t_UT_up != ""]

monomer_a53t_UT_down <- read.csv("./OurData/Invitro/protein_coding_monomer.csv") %>% 
  filter(reg=="down") %>% filter(comparison=="a53t vs ut") %>% unique() %>% dplyr::select(external_gene_name)
monomer_a53t_UT_down <- monomer_a53t_UT_down[monomer_a53t_UT_down != ""]

monomer_a53t_WT_up <- read.csv("./OurData/Invitro/protein_coding_monomer.csv") %>% 
  filter(reg=="up") %>% filter(comparison=="a53t vs wt") %>% unique() %>% dplyr::select(external_gene_name)
monomer_a53t_WT_up <- monomer_a53t_WT_up[monomer_a53t_WT_up != ""]

monomer_a53t_WT_down <- read.csv("./OurData/Invitro/protein_coding_monomer.csv") %>% 
  filter(reg=="down") %>% filter(comparison=="a53t vs wt") %>% unique() %>% dplyr::select(external_gene_name)
monomer_a53t_WT_down <- monomer_a53t_WT_down[monomer_a53t_WT_down != ""]

oligomer_up <- read.csv("./OurData/Invitro/protein_coding_oligomer.csv") %>% 
  filter(reg=="up") %>% unique() %>% dplyr::select(external_gene_name)
oligomer_up <- oligomer_up[oligomer_up != ""]

oligomer_down <- read.csv("./OurData/Invitro/protein_coding_oligomer.csv") %>% 
  filter(reg=="down") %>%  unique() %>% dplyr::select(external_gene_name)
oligomer_down <- oligomer_down[oligomer_down != ""]

mutation_up <- read.csv("./OurData/Invitro/protein_coding_mutation.csv") %>% 
  filter(reg=="up") %>% filter(comparison=="a53t vs ctrl (ut)") %>%  unique() %>% dplyr::select(external_gene_name)
mutation_up <- mutation_up[mutation_up != ""]

mutation_down <- read.csv("./OurData/Invitro/protein_coding_mutation.csv") %>% 
  filter(reg=="down") %>% filter(comparison=="a53t vs ctrl (ut)") %>%  unique() %>% dplyr::select(external_gene_name)
mutation_down <- mutation_down[mutation_down != ""]


# These are actually 3 different experiments - getting split up now into monomer WT, monomer A53T, oligomer, Patient - diff protein species 

invitro_mono <- list(monomer_wt_up,monomer_wt_down,monomer_a53t_UT_up,monomer_a53t_UT_down,monomer_a53t_WT_up,monomer_a53t_WT_down)
names(invitro_mono) <- c("monomer_wt_up","monomer_wt_down","monomer_a53t_UT_up","monomer_a53t_UT_down","monomer_a53t_WT_up","monomer_a53t_WT_down") 

invitro_oligomer <- list(oligomer_up,oligomer_down)
names(invitro_oligomer) <- c("oligomer_up","oligomer_down") 

invitro_mutation <- list(mutation_up,mutation_down)
names(invitro_mutation) <- c("mutation_up","mutation_down") 

```

2. Invitro universes - 3 of these 

```{r}
universe_invitro_monomer <- read.csv("./OurData/Invitro/protein_coding_monomer.csv") %>% select(external_gene_name) %>% unique() %>% nrow()
universe_invitro_mutation <- read.csv("./OurData/Invitro/protein_coding_mutation.csv") %>% select(external_gene_name) %>% unique() %>% nrow()
universe_invitro_oligomer <- read.csv("./OurData/Invitro/protein_coding_oligomer.csv") %>% select(external_gene_name) %>% unique() %>% nrow()
```

*NOW overlapping our in vitro datasets to the DAM profiles*

1. Monomer dataset vs. external DAM 

Adjusting within the external datasets 
Includes both up and down 
universe monomer specific 
calculates Szymkiewicz–Simpson overlap intersection/min of A and B 

```{r}
#| label: Overlap - heatmap invitro monomer 
#| error: false
#| warning: false
#| echo: false
#| output: true

result5 <- Overlap_HLC_func(list1 = invitro_mono,
                            list2=all_external,
                            universe=universe_invitro_monomer,
                            nadj=3,
                            trunc=FALSE, 
                            plot=FALSE,
                            save_res = "./results/result5.csv")

```

Plotting Monomer dataset but just showing upregulated overlaps 

```{r}

result6 <- Overlap_HLC_func(list1 = invitro_mono,
                            list2=all_external,
                            universe=universe_invitro_monomer,
                            nadj=3,
                            trunc=TRUE, 
                            plot=TRUE,
                            trunc_col = c("DAM_Down", "HAM_Down"),
                            trunc_row = c("monomer_wt_down", "monomer_a53t_UT_down","monomer_a53t_WT_down"),
                            plotmax = 0.5,
                            list1_title = "In vitro microglia \n + monomeric protein",
                            split = c(rep("Keren-Shaul 2017", 1),rep("Srinivasan 2020", 1),rep("Martins-Ferreira 2025", 4)), 
                            tidy_col = c("DAM", "HAM", "HuMicA AD DAM", "HuMicA LBD DAM", "HuMicA AD DIM", "HuMicA LBD DIM"),
                            tidy_row = c("WT vs. UT", "A53T vs. UT", "A53T vs. WT"),
                            save_res = "./results/result6.csv",
                            save_fig = "./results/result6.svg",
                            width_fig = 7,
                            height_fig = 4)
```

2. Mutation dataset 

```{r}
#| label: Overlap - heatmap invitro mutation 
#| error: false
#| warning: false
#| echo: false
#| output: true

result7 <- Overlap_HLC_func(list1 = invitro_mutation,
                            list2=all_external,
                            universe=universe_invitro_mutation,
                            nadj=3,
                            trunc=FALSE, 
                            plot=FALSE,
                            save_res = "./results/result7.csv")
```

Mutation dataset but just showing upregulated overlaps 

```{r}
result8 <- Overlap_HLC_func(list1 = invitro_mutation,
                            list2=all_external,
                            universe=universe_invitro_mutation,
                            nadj=3,
                            trunc=TRUE, 
                            plot=TRUE,
                            trunc_col = c("DAM_Down", "HAM_Down"),
                            trunc_row = c("mutation_down"),
                            plotmax = 0.5,
                            list1_title = "In vitro microglia \n SNCA A53T vs. Control",
                            split = c(rep("Keren-Shaul 2017", 1),rep("Srinivasan 2020", 1),rep("Martins-Ferreira 2025", 4)),
                            name_trunc = "SNCA A53T vs. Control", 
                            tidy_col = c("DAM", "HAM", "HuMicA AD DAM", "HuMicA LBD DAM", "HuMicA AD DIM", "HuMicA LBD DIM"),
                            save_res = "./results/results8.csv",
                            save_fig = "./results/result8.svg",
                            width_fig = 7,
                            height_fig = 3)

```

3.Oligomer dataset 

```{r}
#| label: Overlap - heatmap invitro oligomer 
#| error: false
#| warning: false
#| echo: false
#| output: true

result9 <- Overlap_HLC_func(list1 = invitro_oligomer,
                            list2=all_external,
                            universe=universe_invitro_oligomer,
                            nadj=3,
                            trunc=FALSE, 
                            plot=FALSE,
                            save_res = "./results/result9.csv")

```

Oligomer dataset but just showing upregulated overlaps 

```{r}
result10 <- Overlap_HLC_func(list1 = invitro_oligomer,
                            list2=all_external,
                            universe=universe_invitro_oligomer,
                            nadj=3,
                            trunc=TRUE, 
                            plot=TRUE,
                            trunc_col = c("DAM_Down", "HAM_Down"),
                            trunc_row = c("oligomer_down"),
                            plotmax = 0.5,
                            list1_title = "In vitro microglia \n + Oligomeric Protein",
                            split = c(rep("Keren-Shaul 2017", 1),rep("Srinivasan 2020", 1),rep("Martins-Ferreira 2025", 4)),
                            name_trunc = "WT vs. UT",
                            tidy_col = c("DAM", "HAM", "HuMicA AD DAM", "HuMicA LBD DAM", "HuMicA AD DIM", "HuMicA LBD DIM"),
                            save_res = "./results/result10.csv",
                            save_fig = "./results/result10.svg",
                            width_fig = 7,
                            height_fig = 3)

```



*NOW overlapping our in vitro datasets to our in vivo bulk RNAseq brain*

Do our in vitro datasets overlap with the brain? 
Doing this separate for each of the asyn species
The universes will be what is picked up in both the invitro and bulk data 

Defining universes 

```{r}
universe_bulk <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>% 
  dplyr::select(SYMBOL) %>% unique() 

universe_invitro_monomer <- read.csv("./OurData/Invitro/protein_coding_monomer.csv") %>% select(external_gene_name) %>% unique() 
universe_invitro_mutation <- read.csv("./OurData/Invitro/protein_coding_mutation.csv") %>% select(external_gene_name) %>% unique() 
universe_invitro_oligomer <- read.csv("./OurData/Invitro/protein_coding_oligomer.csv") %>% select(external_gene_name) %>% unique() 

universe_intersect_bulk_monomer <- intersect(universe_bulk$SYMBOL,universe_invitro_monomer$external_gene_name) %>% length()
universe_intersect_bulk_mutation <- intersect(universe_bulk$SYMBOL, universe_invitro_mutation$external_gene_name) %>% length()
universe_intersect_bulk_oligomer <- intersect(universe_bulk$SYMBOL, universe_invitro_oligomer$external_gene_name) %>% length()

```


1. Do monomer datasets overlap with the brain? 
- stats for all but plotted just up
```{r}
result11_all <- Overlap_HLC_func(list1 = bulk_all,
                            list2=invitro_mono,
                            universe=universe_intersect_bulk_monomer,
                            nadj=1,
                            trunc=FALSE, 
                            plot=FALSE,
                            save_res = "./results/result11_all.csv")

result11 <- Overlap_HLC_func(list1 = bulk_all,
                            list2=invitro_mono,
                            universe=universe_intersect_bulk_monomer,
                            nadj=1,
                            trunc=TRUE, 
                            plot=TRUE,
                            trunc_col = c("monomer_wt_down", "monomer_a53t_UT_down", "monomer_a53t_WT_down"),
                            trunc_row = c("Collapsed_down", "Cortical_down", "Subcortical_down"),
                            plotmax = 0.5,
                            list1_title = "Bulk RNA seq - upregulated", 
                            tidy_row =  c("Collapsed Brain", "Cortical", "Subcortical"),
                            tidy_col = c("WT vs. UT", "A53T vs. UT", "A53T vs. WT"),
                            save_res = "./results/result11.csv",
                            save_fig = "./results/result11.svg",
                            width_fig = 6,
                            height_fig = 4)
```

2. Do mutation datasets overlap with the brain?

- stats has it all but only up shown

```{r}
result12_all <- Overlap_HLC_func(list1 = bulk_all,
                            list2=invitro_mutation,
                            universe=universe_intersect_bulk_mutation,
                            nadj=1,
                            trunc=FALSE, 
                            plot=FALSE,
                            save_res = "./results/result12_all.csv")

result12 <- Overlap_HLC_func(list1 = bulk_all,
                            list2=invitro_mutation,
                            universe=universe_intersect_bulk_mutation,
                            nadj=1,
                            trunc=TRUE, 
                            plot=TRUE,
                            trunc_col = c("mutation_down"),
                            trunc_row = c("Collapsed_down", "Cortical_down", "Subcortical_down"),
                            list1_title = "In vitro microglia \n SNCA A53T vs. Control - Upregulated",
                            plotmax = 0.5,
                            name_trunc = "SNCA A53T vs. Control",
                            tidy_col =  c("Collapsed Brain", "Cortical", "Subcortical"),
                            save_res = "./results/result12.csv",
                            save_fig = "./results/result12.svg",
                            width_fig = 6,
                            height_fig = 3)
```

3. Do oligomer datasets overlap with the brain?

```{r}

result13_all <- Overlap_HLC_func(list1 = bulk_all,
                            list2=invitro_oligomer,
                            universe=universe_intersect_bulk_oligomer,
                            nadj=1,
                            trunc=FALSE, 
                            plot=FALSE,
                            save_res = "./results/result13_all.csv")

result13 <- Overlap_HLC_func(list1 = bulk_all,
                            list2=invitro_oligomer,
                            universe=universe_intersect_bulk_oligomer,
                            nadj=1,
                            trunc=TRUE, 
                            plot=TRUE,
                            trunc_col = c("oligomer_down"),
                            trunc_row = c("Collapsed_down", "Cortical_down", "Subcortical_down"),
                            plotmax = 0.5,
                            name_trunc = "WT vs. UT",
                            tidy_col =  c("Collapsed Brain", "Cortical", "Subcortical"),
                            list1_title = "In vitro microglia \n  + Oligomeric protein - Upregulated",
                            save_res = "./results/result13.csv",
                            save_fig = "./results/result13.svg",
                            width_fig = 6,
                            height_fig = 3)
```

#Next up - what about asyn unique genes#

Looking at upregulated genes from our invitro datasets : 
A53T patient vs. control 
A53T monomer vs. UT 
A53T monomer vs. WT monomer 
WT oligomer vs. UT

Then looked at the union with Keren-Shaul DAM upregulated genes - those not in the union = unique to alpha syn

```{r}
unique_up_monomerA53T_vs_UT <- setdiff(monomer_a53t_UT_up,DAM_Up)
unique_up_monomerA53T_vs_WT <- setdiff(monomer_a53t_WT_up,DAM_Up)
unique_up_oligomer <- setdiff(oligomer_up,DAM_Up)
unique_up_A53Tpatient <- setdiff(mutation_up,DAM_Up)

save <- as.data.frame(unique_up_oligomer)
write_csv(save,"./results/noDAM_yesOligomer_genes.csv")

unique_monomer <- list(unique_up_monomerA53T_vs_UT,unique_up_monomerA53T_vs_WT)
unique_patient <- list(unique_up_A53Tpatient)
unique_oligomer <- list(unique_up_oligomer)

names(unique_monomer) <- c("A53T monomer vs. UT", "A53T monomer vs. WT monomer" )
names(unique_patient) <- c("SNCA A53T vs. Control")
names(unique_oligomer) <- c("WT Oligomer vs. UT")

unique_total_asyn <- c(unique_up_monomerA53T_vs_UT,unique_up_monomerA53T_vs_WT,unique_up_oligomer,unique_up_A53Tpatient) %>% unique()
unique_total_asyn <- list(unique_total_asyn)
names(unique_total_asyn) <- c("asyn signature")
```

Then did an overlap analysis with our bulk data 
This answers whether what we see in the dish that is uniquely asyn in the brain

Universe here - the specific invitro dataset overlapped with the bulk dataset and took the union 

1. Defining universe 

```{r}
universe_bulk <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>% 
  dplyr::select(SYMBOL) %>% unique()
universe_invitro_monomer <- read.csv("./OurData/Invitro/protein_coding_monomer.csv") %>% select(external_gene_name) %>% unique()
universe_invitro_mutation <- read.csv("./OurData/Invitro/protein_coding_mutation.csv") %>% select(external_gene_name) %>% unique()
universe_invitro_oligomer <- read.csv("./OurData/Invitro/protein_coding_oligomer.csv") %>% select(external_gene_name) %>% unique()

combined <- c(universe_invitro_monomer$external_gene_name,universe_invitro_mutation$external_gene_name,universe_invitro_oligomer$external_gene_name) %>% unique()
combined_universe <- intersect(combined,universe_bulk$SYMBOL) %>% length()

union_monomer <- intersect(universe_bulk$SYMBOL,universe_invitro_monomer$external_gene_name) %>% length()
union_mutation <- intersect(universe_bulk$SYMBOL,universe_invitro_mutation$external_gene_name) %>% length()
union_oligomer <- intersect(universe_bulk$SYMBOL,universe_invitro_oligomer$external_gene_name) %>% length()

rm(universe_bulk, universe_invitro_monomer, universe_invitro_mutation, universe_invitro_oligomer)
```

2. Performing Overlap for monomer asyn specific to our bulk data 

```{r}
result14 <- Overlap_HLC_func(list1 = bulk_up,
                            list2=unique_monomer,
                            universe=union_monomer,
                            nadj=1,
                            trunc=FALSE, 
                            plot=TRUE,
                            plotmax = 0.5,
                            tidy_row =  c("Collapsed Brain", "Cortical", "Subcortical"),
                            list1_title = "Bulk RNAseq PD vs. Control",
                            tidy_col = c("A53T vs. UT", "A53T vs. WT"),
                            save_res = "./results/result14.csv",
                            save_fig = "./results/result14.svg",
                            width_fig = 7,
                            height_fig = 4)

```


3. Performing Overlap for mutation asyn specific to our bulk data 

```{r}
result15 <- Overlap_HLC_func(list1 = bulk_up,
                            list2=unique_patient,
                            universe=union_mutation,
                            nadj=1,
                            trunc=FALSE, 
                            plot=TRUE,
                            plotmax = 0.5,
                            tidy_row =  c("Collapsed Brain", "Cortical", "Subcortical"),
                            list1_title = "Bulk RNAseq PD vs. Control",
                            save_res = "./results/result15.csv",
                            save_fig = "./results/result15.svg",
                            width_fig = 6,
                            height_fig = 4)

```


4. Performing Overlap for oligomer asyn specific to our bulk data 

```{r}
result16 <- Overlap_HLC_func(list1 = bulk_up,
                            list2=unique_oligomer,
                            universe=union_oligomer,
                            nadj=1,
                            trunc=FALSE, 
                            plot=TRUE,
                            plotmax = 0.5,
                            list1_title = "Bulk RNAseq PD vs. Control",
                            tidy_row =  c("Collapsed Brain", "Cortical", "Subcortical"),
                            save_res = "./results/result16.csv",
                            save_fig = "./results/result16.svg",
                            width_fig = 6,
                            height_fig = 4)

```

#Pathway analysis#

Looking at those that are in the intersection of the significant oligomer overlap analysis 
what are they enriched for? 

```{r}
overlap <- newGOM(bulk_up, unique_oligomer, genome.size=union_oligomer)

inter_oligomer_collapsed <- overlap@go.nested.list$`WT Oligomer vs. UT`$Collapsed_up@intersection
inter_oligomer_ctx <- overlap@go.nested.list$`WT Oligomer vs. UT`$Cortical_up@intersection
inter_oligomer_subctx <- overlap@go.nested.list$`WT Oligomer vs. UT`$Subcortical_up@intersection

write.csv(inter_oligomer_collapsed,"./results/intersection_uniqueoligomer_collapsed_uponly.csv")
write.csv(inter_oligomer_ctx, "./results/intersection_uniqueoligomer_cortical_uponly.csv")
write.csv(inter_oligomer_subctx, "./results/intersection_uniqueoligomer_subcortical_uponly.csv")

GO_inter_oligomer_collapsed <- enrichGO(gene=inter_oligomer_collapsed,keyType = "SYMBOL", OrgDb = org.Hs.eg.db, ont="ALL")
GO_inter_oligomer_ctx <- enrichGO(gene=inter_oligomer_ctx,keyType = "SYMBOL", OrgDb = org.Hs.eg.db, ont="ALL")
GO_inter_oligomer_subctx <- enrichGO(gene=inter_oligomer_subctx,keyType = "SYMBOL", OrgDb = org.Hs.eg.db, ont="ALL")

GO_inter_oligomer_collapsed@result <- subset(GO_inter_oligomer_collapsed@result,ONTOLOGY %in% c("BP", "MF"))
GO_inter_oligomer_ctx@result <- subset(GO_inter_oligomer_ctx@result,ONTOLOGY %in% c("BP", "MF"))
GO_inter_oligomer_subctx@result <- subset(GO_inter_oligomer_subctx@result,ONTOLOGY %in% c("BP", "MF"))

write.csv(GO_inter_oligomer_collapsed@result,"./results/intersection_uniqueoligomer_collapsed_uponly_RESULTS.csv")
write.csv(GO_inter_oligomer_ctx@result, "./results/intersection_uniqueoligomer_cortical_uponly_RESULTS.csv")
write.csv(GO_inter_oligomer_subctx@result, "./results/intersection_uniqueoligomer_subcortical_uponly_RESULTS.csv")


```


```{r}
GO_collapsed <- dotplot(GO_inter_oligomer_collapsed,showCategory = 10, split = "ONTOLOGY") + facet_grid(ONTOLOGY ~ ., scales = "free_y", space = "free_y")
ggsave(
  filename = "./results/GO_oligomer_collapsed.svg",
  plot = GO_collapsed,
  device = "svg",
  width = 7,
  height = 11
)

GO_Cortical <- dotplot(GO_inter_oligomer_ctx,showCategory = 10, split = "ONTOLOGY") + facet_grid(ONTOLOGY ~ ., scales = "free_y", space = "free_y")
ggsave(
  filename = "./results/GO_oligomer_cortical.svg",
  plot = GO_Cortical,
  device = "svg",
  width = 7,
  height = 11
)

GO_subcortical <- dotplot(GO_inter_oligomer_subctx,showCategory = 10, split = "ONTOLOGY") + facet_grid(ONTOLOGY ~ ., scales = "free_y", space = "free_y")
ggsave(
  filename = "./results/GO_oligomer_subcortical.svg",
  plot = GO_subcortical,
  device = "svg",
  width = 7,
  height = 11
)
```

5. Regardless of source the asyn signature across all of the invitro datasets 

```{r}
result17 <- Overlap_HLC_func(list1 = bulk_up,
                            list2=unique_total_asyn,
                            universe=combined_universe,
                            nadj=1,
                            trunc=FALSE, 
                            plot=TRUE,
                            plotmax = 0.5,
                            tidy_row =  c("Collapsed Brain", "Cortical", "Subcortical"),
                            list1_title = "Bulk RNAseq PD vs. Control",
                            save_res = "./results/result17.csv",
                            save_fig = "./results/result17.svg",
                            width_fig = 6,
                            height_fig = 4)

```


Ok now what about in vitro tau datasets? 

Taking the data from the folllowing paper: 

Kreger Karabova et al 2026 (Sally Cowley) - tau 
monomeric (rTauM) - 5 down regulated genes only HSPG2, IFITM10,  COL1A1, COL5A1, APBA3
fibrillar (rTauF) - 87 down and 96 up 
tau from brains (hTau) - 29 up and 23 down 


```{r}
Kreger_universe_1 <-  read.csv("./Karabova_2026_ctrl_fibril.csv") %>%  select(X) %>% unique()
Kreger_universe_2 <-  read.csv("./Karabova_2026_hdTau_hTau.csv") %>%  select(X) %>% unique()
Kreger_universe_3 <-  read.csv("./Karabova_2026_monomer_ctrl.csv") %>%  select(X) %>% unique()
Kreger_universe <- c(Kreger_universe_1$X, Kreger_universe_2$X, Kreger_universe_3$X) %>% unique()

rTauF_vs_vehicle_down <- read.csv("./Karabova_2026_ctrl_fibril.csv") %>% filter(padj<0.05) %>% filter(log2FoldChange < -0.5)
rTauF_vs_vehicle_up <- read.csv("./Karabova_2026_ctrl_fibril.csv") %>% filter(padj<0.05) %>% filter(log2FoldChange > 0.5)
rTauM_vs_vehicle_down <- read.csv("./Karabova_2026_monomer_ctrl.csv") %>% filter(padj<0.05) %>% filter(log2FoldChange < -0.5)
#rTauM_vs_vehicle_up <- read.csv("./Karabova_2026_monomer_ctrl.csv") %>% filter(padj<0.05) %>% filter(log2FoldChange > 0.5)
hTau_up <- read.csv("./Karabova_2026_hdTau_hTau.csv") %>% filter(padj<0.05) %>% filter(log2FoldChange > 0.5)
hTau_down <- read.csv("./Karabova_2026_hdTau_hTau.csv") %>% filter(padj<0.05) %>% filter(log2FoldChange < -0.5)

Tau <- list(rTauM_vs_vehicle_down$X, rTauF_vs_vehicle_down$X,rTauF_vs_vehicle_up$X,  hTau_down$X, hTau_up$X)
names(Tau) <- c("Tau Monomer vs. UT - Down", "Tau Fibril vs. UT - Down", "Tau Fibril vs. UT - Up","hTau - Down", "hTau - Up")
```

Defining universes 

```{r}
universe_invitro_monomer <- read.csv("./OurData/Invitro/protein_coding_monomer.csv") %>% select(external_gene_name) %>% unique()
universe_invitro_mutation <- read.csv("./OurData/Invitro/protein_coding_mutation.csv") %>% select(external_gene_name) %>% unique()
universe_invitro_oligomer <- read.csv("./OurData/Invitro/protein_coding_oligomer.csv") %>% select(external_gene_name) %>% unique()

union_monomer_wtau <- intersect(Kreger_universe,universe_invitro_monomer$external_gene_name) %>% length()
union_mutation_wtau <- intersect(Kreger_universe,universe_invitro_mutation$external_gene_name) %>% length()
union_oligomerwtau <- intersect(Kreger_universe,universe_invitro_oligomer$external_gene_name) %>% length()

universe_bulk_2 <- read.csv("./OurData/Bulk/dge_all_Gene_panel_studies_lookups_added.csv") %>% 
  dplyr::select(SYMBOL) %>% unique()
union_bulk_tau <- intersect(Kreger_universe,universe_bulk_2$SYMBOL) %>% length()

rm(universe_invitro_monomer, universe_invitro_mutation, universe_invitro_oligomer,universe_bulk_2)
```


Monomer asyn with Tau 

```{r}
result18 <- Overlap_HLC_func(list1 = Tau,
                            list2=invitro_mono,
                            universe=union_monomer_wtau,
                            nadj=1,
                            trunc=FALSE, 
                            plot=TRUE,
                            plotmax = 0.6,
                            list1_title = "Kreger - tau",
                            tidy_col = c("WT vs. UT - Up", "WT vs. UT - Down", "A53T vs. UT - Up", "A53T vs. UT - Down", "A53T vs. WT - Up", "A53T vs. WT - Down"),
                            save_res = "./results/result18.csv",
                            save_fig = "./results/result18.svg",
                            width_fig = 7,
                            height_fig = 4)
```
Just upregulated from above - but same stats underneath 

```{r}
result19 <- Overlap_HLC_func(list1 = Tau,
                            list2=invitro_mono,
                            universe=union_monomer_wtau,
                            nadj=1,
                            trunc=TRUE, 
                            plot=TRUE,
                            trunc_col = c("monomer_wt_down", "monomer_a53t_UT_down", "monomer_a53t_WT_down"),
                            trunc_row = c("Tau Monomer vs. UT - Down", "Tau Fibril vs. UT - Down", "hTau - Down"),
                            plotmax = 0.5,
                            tidy_col = c("WT vs. UT", "A53T vs. UT", "A53T vs. WT"),
                            tidy_row = c("Tau Fibril vs. UT", "hTau"), 
                            list1_title = "Kreger Tau - Upregulated",
                            save_res = "./results/result19.csv",
                            save_fig = "./results/result19.svg",
                            width_fig = 7,
                            height_fig = 4)


```

Mutation 

```{r}
result20 <- Overlap_HLC_func(list1 = Tau,
                            list2=invitro_mutation,
                            universe=union_mutation_wtau,
                            nadj=1,
                            trunc=FALSE, 
                            plot=TRUE,
                            plotmax = 0.5, 
                            tidy_col = c("SNCA A53T vs. Control - Up", "SNCA A53T vs. Control - Down"),
                            list1_title = "Kreger - Tau",
                            save_res = "./results/result20.csv",
                            save_fig = "./results/result20.svg",
                            width_fig = 7,
                            height_fig = 4)
```
Just upregulated from above - but same stats underneath 

```{r}
result21 <- Overlap_HLC_func(list1 = Tau,
                            list2=invitro_mutation,
                            universe=union_mutation_wtau,
                            nadj=1,
                            trunc=TRUE, 
                            plot=TRUE,
                            trunc_col = c("mutation_down"),
                            trunc_row = c("Tau Monomer vs. UT - Down", "Tau Fibril vs. UT - Down", "hTau - Down"),
                            plotmax = 0.5,
                            name_trunc = "SNCA A53T vs. Control", 
                            list1_title = "In vitro microglia", 
                            tidy_col = c("Tau Fibril vs. UT", "hTau"),
                            save_res = "./results/result21.csv",
                            save_fig = "./results/result21.svg",
                            width_fig = 6,
                            height_fig = 4)

```


Oligomer 

```{r}
result22 <- Overlap_HLC_func(list1 = Tau,
                            list2=invitro_oligomer,
                            universe=union_oligomerwtau,
                            nadj=1,
                            trunc=FALSE, 
                            plot=TRUE,
                            plotmax = 0.5, 
                            tidy_col = c("WT Oligomer vs. UT - Up", "WT Oligomer vs. UT - Down"), 
                            list1_title = "Kreger - tau",
                            save_res = "./results/result22.csv",
                            save_fig = "./results/result22.svg",
                            width_fig = 7,
                            height_fig = 4)
```
Just upregulated from above - but same stats underneath 

```{r}
result23 <- Overlap_HLC_func(list1 = Tau,
                            list2=invitro_oligomer,
                            universe=union_oligomerwtau,
                            nadj=1,
                            trunc=TRUE, 
                            plot=TRUE,
                            trunc_col = c("oligomer_down"),
                            trunc_row = c("Tau Monomer vs. UT - Down", "Tau Fibril vs. UT - Down", "hTau - Down"),
                            plotmax = 0.5,
                            name_trunc = "WT Oligomer vs. UT",
                            tidy_col = c("Tau Fibril vs. UT", "hTau"),
                            list1_title = "In vitro microglia",
                            save_res = "./results/result23.csv",
                            save_fig = "./results/result23.svg",
                            width_fig = 6,
                            height_fig = 3)


```

OK what about those unique asyn that were identified earlier - seperate from DAM and how they overlap with the tau signature? - just upregulated for both in here 

```{r}
Tau_UP <- list(rTauF_vs_vehicle_up$X, hTau_up$X)
names(Tau_UP) <- c("Tau Fibril vs. UT", "hTau")

result24 <- Overlap_HLC_func(list1 = Tau_UP,
                            list2=unique_monomer,
                            universe=union_monomer_wtau,
                            nadj=1,
                            trunc=FALSE, 
                            plot=TRUE,
                            plotmax = 0.5,
                            tidy_col = c("A53T vs. UT", "A53T vs. WT"), 
                            list1_title = "Kreger - Tau",
                            save_res = "./results/result24.csv",
                            save_fig = "./results/result24.svg",
                            width_fig = 7,
                            height_fig = 4)
                        
```


```{r}
result25 <- Overlap_HLC_func(list1 = Tau_UP,
                            list2=unique_patient,
                            universe=union_mutation_wtau,
                            nadj=1,
                            trunc=FALSE, 
                            plot=TRUE,
                            plotmax = 0.5, 
                            list1_title = "Tau - Kreger",
                            save_res = "./results/result25.csv",
                            save_fig = "./results/result25.svg",
                            width_fig = 6,
                            height_fig = 4)
```


Oligomer

```{r}
result26 <- Overlap_HLC_func(list1 = Tau_UP,
                            list2=unique_oligomer,
                            universe=union_oligomerwtau,
                            nadj=1,
                            trunc=FALSE, 
                            plot=TRUE,
                            plotmax = 0.5, 
                            list1_title = "Kreger - Tau",
                            save_res = "./results/result26.csv",
                            save_fig = "./results/result26.svg",
                            width_fig = 6,
                            height_fig = 4)

```


All tau vs. all bulk 

```{r}

result27_all <- Overlap_HLC_func(list1 = bulk_all,
                            list2=Tau,
                            universe=union_bulk_tau,
                            nadj=1,
                            trunc=FALSE, 
                            plot=TRUE,
                            save_res = "./results/result27_all.csv",
                            width_fig = 7,
                            height_fig = 4,
                            plotmax = 0.5,
                            save_fig = "./results/result27_all.svg",
                            list1_title = "Bulk RNAseq PD vs. Control",
                            tidy_col = c("Tau Monomer vs. UT - Down", "Tau Fibril vs. UT - Down","Tau Fibril vs. UT - Up", "hTau - Down", "hTau - Up"), 
                            tidy_row = c("Collapsed Brain - Up", "Collapsed Brain - Down", "Cortical - Up", "Cortical - Down", "Subcortical - Up", "Subcortical - Down"))

result27 <- Overlap_HLC_func(list1 = bulk_all,
                            list2=Tau,
                            universe=union_bulk_tau,
                            nadj=1,
                            trunc=TRUE, 
                            plot=TRUE,
                            plotmax = 0.5,
                            trunc_col = c("Tau Monomer vs. UT - Down", "Tau Fibril vs. UT - Down", "hTau - Down"),
                            trunc_row = c("Collapsed_down","Cortical_down", "Subcortical_down"), 
                            tidy_col = c("Tau Fibril vs. UT", "hTau"), 
                            tidy_row = c(" Collapsed Brain", "Cortical", "Subcortical"), 
                            list1_title = "Bulk RNAseq PD vs. Control",
                            save_res = "./results/result27.csv",
                            save_fig = "./results/result27.svg",
                            width_fig = 7,
                            height_fig = 4)

```

